\cvsection{Work Experience}
\begin{cventries}
  \cventry
  {Computer Vision Engineer Intern} % Job title
  {Conxai} % Organization
  {Munich, Germany} % Location
  {Dec 2020 - Feb 2021} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Responsible for designing and implementing an end to end \textbf{Data
      pipeline} to process raw construction videos and annotate for Object Detection in the
      construction field.}
    \item {Developed a web application using \textbf{Django} to control and
    manage the \textbf{Data pipeline} and \textbf{Machine Learning pipeline}.}
    \item {Implemented an object detection pipeline using \textbf{MaskRCNN} for
    detecting various objects that are related to different construction
    process.}
    \item {Implemented \textbf{PlaneRCNN} a plane detection model in
    \textbf{PyTorch} for 3D scene understanding in construction sites.}
    \item {Developed a photo documentation using 360 images of a construction
    process using \textbf{marzipano}. Integrated object detection inferences into photo documentation. }
  \end{cvitems}
  }

  \cventry
  {Master Thesis} % Empty position
  {German Aerospace Center (DLR)} % Project
  {Oberpfaffenhofen, Germany} % Empty location
  {March 2020 - Nov 2020} % Empty date
  {
  \begin{cvitems} % Description(s) bullet points
    \item {Topic: 3D Mesh Segmentation using Transformer Based Graph Operations - Prof. Rudolph Triebel}
    \item {Designed a new graph convolution operation based on the famous
    \textbf{transformer} architecture using the attention mechanism}
    \item {Tested the effect of positional encoding on the convolution layer for
    the task of \textbf{3D mesh segmentation} on \textbf{ShapeNet} and
    \textbf{Coseg} datasets}
    \item {Implemented a custom \textbf{c++/cuda extension} to \textbf{PyTorch}
    to dynamically calculate neighbors up to a certain depth on GPU, to apply
    the concept of atrous convolution.}
  \end{cvitems}
  }

  \cventry
  {Work Student} % Job title
  {German Aerospace Center (DLR)} % Organization
  {Oberpfaffenhofen, Germany} % Location
  {June 2019 - Feb. 2020} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed an algorithm to compress a \textbf{TSDF(Truncated Sign
    Distance Field)} volume of a 3D scene by 64 times using \textbf{generative
    models}}
    \item {Experimented with different generative model architectures
    \textbf{(GAN, Generative Latent Optimization (GLO), Auto Encoders)} and
    training methods using \textbf{TensorFlow}}
    \item {Designed various \textbf{loss shaping} strategies to improve the
    reconstruction from the compressed TSDF}
    \item {Incorporated semantic information to the encodings to further improve the reconstruction}
    \item {Helped writing code to generate segmentation data for the TSDF
    volumes from 3D meshes efficiently using \textbf{C++}}
  \end{cvitems}
  }

  \cventry
  {Software Development Engineer} % Job title
  {Flipkart} % Organization
  {Bangalore, India} % Location
  {June 2017 - August 2018} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed a \textbf{Django} based web application for the support
    team to automate the debugging of an issue raised by the customer.}
    \item {Used \textbf{Docker} to create images of the application and host the
    web app internally}
    \item {Built a Java \textbf{Spring} application to process huge Excel files
    of product information from the sellers and update them in the Flipkart
    Seller system.}
    \item {Used \textbf{Spring Batch} Remote Chunking (master slave) to
    distribute the processing of huge files to the slaves using \textbf{Apache
    Kafka} as a messaging system between the master and the slave.}
    \item {Used \textbf{Apache Kafka} to maintain priority queues to prioritize
    the processing of the files of premium sellers.}
  \end{cvitems}
  }

  \cventry
  {Quantitative Analyst} % Job title
  {Dolat Capital} % Organization
  {Mumbai, India} % Location
  {July 2016 - May 2017} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Helped developing various strategies to trade Stock Options, Futures and Equity at very high frequency profitably.}
    \item {Built a linear regression model with features generated using various technical indicators like Bollinger Bands, Z-score, Weighted average price.}
    \item {Used multiple feature and model filtering techniques such as p-value, t-test, z-test, R-Squared, Variation Inflation Factor.}
  \end{cvitems}
  }
  % \cventry
  % {Software Developer Intern} % Job title
  % {Microsoft India Development Center} % Organization
  % {Hyderabad, India} % Location
  % {May. 2015 - July. 2015} % Date(s)
  % {
  % \begin{cvitems} % Description(s) of tasks/responsibilities
  %   \item {Developed an Android app which enables the user to explore and obtain all required details about attractions nearby, or in any other city  }
  %   \item {Extended the app to provide popular phrases pertaining to that region that could be useful along with their translation and transliteration}
  %   \item {Worked on both front and back-end making use of Model-View-Controller, Entity Framework, ASP.NET, Azure and Python scripts to insert data}
  % \end{cvitems}
  % }
  % \cventry {Software Developer Intern} % Job title {Shearwater} % Organization
  % {Mumbai, India} % Location {May. 2014 - Sept. 2014} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities \item
    %     {Developed an iOS app for users to post about events and their
    %     requirements to be viewed by other users in the same location} \item
    %     {Created social groups and a chat interface for the users to text and
    %     share audio as well as picture messages} \end{cvitems}
    % } 
\end{cventries}
  